---
title: "Checks"
fig-dpi: 300
lightbox: auto
execute:
  cache: false
warning: false
format: 
  html:
   toc: true
code-fold: true
code-tools: true
code-link: true
knitr: 
  opts_chunk: 
   out.width: "120%"
---
  
```{r} 
#| echo: false
#| warning: false
#| error: false

library(tidyverse)
library(hms)
library(rstatix)
library(flextable)
library(reactable)
library(reactablefmtr)
library(pins)

theme_update(text = element_text(size = 12),
             axis.text.x = element_text(size = 12, color = "black"), 
             axis.title.x = element_text(size = 14),
             axis.text.y = element_text(size = 12,  color = "black"), 
             axis.title.y = element_text(size = 14), 
             panel.background = element_blank(),panel.border = element_blank(), 
             panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(), axis.line = element_blank(), 
             axis.ticks.length=unit(.25, "cm"), 
             legend.key = element_rect(fill = "white")) 

board <- board_folder("/Volumes/padlab/study_sensorsinperson/data_processed/datasets/")
data_version <- board %>% pin_meta("redcap_data")

cols = c("sitting", "belly", "crawl", "cruise", "walk")
dates = c("visit_date", "dob", "sit_date", "belly_date", "crawl_date", "cruise_date", "walk_date")
redcap <- board %>% pin_read("redcap_data") %>% 
  select(id:visit_date, sitting:walking_notes) %>% 
  mutate(across(all_of(cols), ~ ifelse(is.na(.x),"Missing",.x))) %>% 
  mutate(across(all_of(cols), ~ factor(.x, levels = c("Missing", "No","Yes")))) %>% 
  mutate(across(all_of(dates), ~ ymd(.x)))
```

| Last updated: `r round(now())` using pinned data version from: `r round(data_version$created)`
| 
|  

## Milestone Checks

### Are any milestones missing?

Any missing entries in the following table must be fixed:

```{r}
#| warning: false
#| error: false

check_missing <- redcap %>% filter(sitting == "Missing" | belly == "Missing" | crawl == "Missing" | cruise == "Missing" | walk == "Missing") %>% 
  select(id, session, all_of(cols))

if (nrow(check_missing) == 0) {
  print("No missing rows")
} else {
  print(check_missing)
}
```

### Are any dates impossible?

Any dates in the following table must be fixed because they occurred after the visit:

```{r}
#| warning: false
#| error: false
check_dates <- redcap %>% filter(sit_date > visit_date | belly_date > visit_date | crawl_date > visit_date | cruise_date > visit_date | walk_date > visit_date) %>% 
  select(id, all_of(dates))

if (nrow(check_dates) == 0) {
  print("No impossible dates")
} else {
  print(check_dates)
}
```

### Are milestone dates consistent across visits?
| &#x2714; Yes, &#x2716; Never Observed, &#x274C; No (Needs to be Fixed)
```{r}
#| warning: false
#| error: false

redcap %>% group_by(id) %>% summarize(Sit = n_distinct(sit_date, na.rm = T), Belly = n_distinct(belly_date, na.rm = T), Crawl = n_distinct(crawl_date, na.rm = T), Cruise = n_distinct(cruise_date, na.rm = T), Walk = n_distinct(walk_date, na.rm = T)) %>% 
  reactable( 
          filterable = TRUE, 
          compact = TRUE,
          striped = TRUE,
          defaultPageSize = 50,
          defaultSorted = c("id"),
          columns = list(
            id = colDef(format = colFormat(digits = 0), maxWidth = 50, align = "left"),
            Sit = colDef(maxWidth = 90, cell = function(value) {if (value == 1) "\u2714\ufe0f" else if (value == 0) "\u2716" else "\u274c"}),
            Belly = colDef(maxWidth = 90, cell = function(value) {if (value == 1) "\u2714\ufe0f" else if (value == 0) "\u2716" else "\u274c"}),
            Crawl = colDef(maxWidth = 90, cell = function(value) {if (value == 1) "\u2714\ufe0f" else if (value == 0) "\u2716" else "\u274c"}),
            Cruise = colDef(maxWidth = 90, cell = function(value) {if (value == 1) "\u2714\ufe0f" else if (value == 0) "\u2716" else "\u274c"}),
            Walk = colDef(maxWidth = 90, cell = function(value) {if (value == 1) "\u2714\ufe0f" else if (value == 0) "\u2716" else "\u274c"})
            ))

```

### Have infants acquired milestones by expected ages?

#### Session 1 (7 months)

```{r}
#| warning: false
#| error: false

summarize_milestones <- function(s) {
  bind_cols(
  {redcap %>% filter(session == s) %>% count(sitting, name = "sit_n", .drop = F)},
  {redcap %>% filter(session == s) %>% count(belly, name = "belly_n", .drop = F)},
  {redcap %>% filter(session == s) %>% count(crawl, name = "hk_n", .drop = F)},
  {redcap %>% filter(session == s) %>% count(cruise, name = "cruise_n", .drop = F)},
  {redcap %>% filter(session == s) %>% count(walk, name = "walk_n", .drop = F)})
}
summarize_milestones(1)
```
Unlikely to be any cruisers or walkers (check anyone who appears in the table below):
```{r}
#| warning: false
#| error: false
check_7 <- redcap %>% filter(session == 1) %>% filter(cruise == "Yes" | walk == "Yes") %>% 
  select(id, session, all_of(cols))
if (nrow(check_7) == 0) {
  print("No flagged rows")
} else {
  print(check_7)
}
```


#### Session 2 (9 months)

```{r}
#| warning: false
#| error: false
summarize_milestones(2)
```
Most infants should be sitting, unlikely to be walking (check anyone who appears in the table below):
```{r}
#| warning: false
#| error: false
check_9 <- redcap %>% filter(session == 2) %>% filter(sitting == "No" | walk == "Yes") %>% 
  select(id, session, all_of(cols))
if (nrow(check_9) == 0) {
  print("No flagged rows")
} else {
  print(check_9)
}
```

#### Session 3 (11 months)

```{r}
#| warning: false
#| error: false
summarize_milestones(3)
```
Most infants should be sitting (check anyone who appears in the table below):
```{r}
#| warning: false
#| error: false
check_11 <- redcap %>% filter(session == 3) %>% filter(sitting == "No") %>% 
  select(id, session, all_of(cols))
if (nrow(check_11) == 0) {
  print("No flagged rows")
} else {
  print(check_11)
}
```

#### Session 4 (13 months)

```{r}
#| warning: false
#| error: false
summarize_milestones(4)
```
Most infants should be sitting and cruising (check anyone who appears in the table below):
```{r}
#| warning: false
#| error: false
check_13 <- redcap %>% filter(session == 4) %>% filter(sitting == "No" | cruise == "No") %>% 
  select(id, session, all_of(cols))
if (nrow(check_13) == 0) {
  print("No flagged rows")
} else {
  print(check_13)
}
```

### Are onset ages within expected ranges?

#### Sitting

Check any of the following (sitting onset < 5 or > 8 months)
```{r}
sit_onset <- redcap %>% select(id, session, dob, sitting, sit_date) %>% 
  filter(sitting == "Yes") %>% group_by(id) %>% slice_max(session) %>% 
  mutate(onset_age = time_length(interval(dob, sit_date),unit = "month")) %>% ungroup()
check_sit <- sit_onset %>% filter(onset_age < 5 | onset_age > 8)
if (nrow(check_sit) == 0) {
  print("No flagged rows")
} else {
  print(check_sit)
}
```

```{r}
ggplot(sit_onset, aes(onset_age)) + geom_histogram(binwidth = .25) + 
  scale_x_continuous(limits = c(3,13), breaks = 3:13, name = "Onset age (mo)") + 
  ggtitle("Sitting onset")
```
#### Belly crawling

Check any of the following (belly onset < 5 or > 8 months)
```{r}
belly_onset <- redcap %>% select(id, session, dob, belly, belly_date) %>% 
  filter(belly == "Yes") %>% group_by(id) %>% slice_max(session) %>% 
  mutate(onset_age = time_length(interval(dob, belly_date),unit = "month")) %>% ungroup()
check_belly <- belly_onset %>% filter(onset_age < 5 | onset_age > 8)
if (nrow(check_belly) == 0) {
  print("No flagged rows")
} else {
  print(check_belly)
}
```

```{r}
ggplot(belly_onset, aes(onset_age)) + geom_histogram(binwidth = .25) + 
  scale_x_continuous(limits = c(3,13), breaks = 3:13, name = "Onset age (mo)") + 
  ggtitle("Belly onset")
```

#### Hands and knees crawling

Check any of the following (crawling onset < 5 or > 11 months)
```{r}
crawl_onset <- redcap %>% select(id, session, dob, crawl, crawl_date) %>% 
  filter(crawl == "Yes") %>% group_by(id) %>% slice_max(session) %>% 
  mutate(onset_age = time_length(interval(dob, crawl_date),unit = "month"))
check_crawl <- crawl_onset %>% filter(onset_age < 5 | onset_age > 11)
if (nrow(check_crawl) == 0) {
  print("No flagged rows")
} else {
  print(check_crawl)
}
```

```{r}
ggplot(crawl_onset, aes(onset_age)) + geom_histogram(binwidth = .25) + 
  scale_x_continuous(limits = c(3,13), breaks = 3:13, name = "Onset age (mo)") + 
  ggtitle("Crawl onset")
```
#### Cruising

Check any of the following (cruising onset < 7 or > 12 months)
```{r}
cruise_onset <- redcap %>% select(id, session, dob, cruise, cruise_date) %>% 
  filter(cruise == "Yes") %>% group_by(id) %>% slice_max(session) %>% 
  mutate(onset_age = time_length(interval(dob, cruise_date),unit = "month"))
check_cruise <- cruise_onset %>% filter(onset_age < 7 | onset_age > 12)
if (nrow(check_cruise) == 0) {
  print("No flagged rows")
} else {
  print(check_cruise)
}
```

```{r}
ggplot(cruise_onset, aes(onset_age)) + geom_histogram(binwidth = .25) + 
  scale_x_continuous(limits = c(3,13), breaks = 3:13, name = "Onset age (mo)") + 
  ggtitle("Cruise onset")
```

#### Walking

Check any of the following (walking onset < 9 or > 16 months)
```{r}
walk_onset <- redcap %>% select(id, session, dob, walk, walk_date) %>% 
  filter(walk == "Yes") %>% group_by(id) %>% slice_max(session) %>% 
  mutate(onset_age = time_length(interval(dob, walk_date),unit = "month"))
check_walk <- walk_onset %>% filter(onset_age < 9 | onset_age > 16)
if (nrow(check_walk) == 0) {
  print("No flagged rows")
} else {
  print(check_walk)
}
```

```{r}
ggplot(walk_onset, aes(onset_age)) + geom_histogram(binwidth = .25) + 
  scale_x_continuous(limits = c(3,13), breaks = 3:13, name = "Onset age (mo)") + 
  ggtitle("Walk onset")
```