---
title: "Sessions"
---

```{r}
#| echo: false
#| warning: false
#| error: false

library(tidyverse)
library(reactable)
library(reactablefmtr)
library(REDCapR)
library(janitor)

uri <- "https://redcap.ucr.edu/api/"
source("api_token.R")


events <- c("visit_1_arm_1", "visit_2_arm_1", "visit_3_arm_1", "visit_4_arm_1")
ds <- redcap_read(redcap_uri = uri, token = api_token, events = events, forms = c("study_outcome", "mo_study_outcome"))$data 
ds <- ds %>% mutate(study_outcome_complete = ifelse(redcap_event_name == "visit_4_arm_1", mo_study_outcome_complete, study_outcome_complete),
                    inclusion = ifelse(redcap_event_name == "visit_4_arm_1", finished_aims, inclusion))
ds <- ds %>% filter(study_outcome_complete != 1) %>% 
  mutate(session = str_remove(str_remove(redcap_event_name, "visit_"),"_arm_1"),
         session = factor(session, levels = c("1","2","3","4"))) %>% 
  select(study_id, session, next_interest, inclusion) %>% 
  rename(Session = inclusion, ID = study_id)

ds <- complete(ds, ID, session) %>% pivot_wider(id_cols = ID, names_from = session, values_from = c("next_interest","Session"))
ds <- ds %>%
  mutate(Session_2 = ifelse(next_interest_1 == 1 & is.na(Session_2), 2, Session_2),
         Session_3 = ifelse(next_interest_2 == 1 & is.na(Session_3), 2, Session_3),
         Session_4 = ifelse(next_interest_3 == 1 & is.na(Session_4), 2, Session_4)) %>% 
  replace_na(list(Session_1 = 0, Session_2 = 0, Session_3 = 0, Session_4 = 0))

ds <- ds %>% mutate(
  In_Person = as.numeric(Session_1 == 1) + as.numeric(Session_2 == 1) + as.numeric(Session_3 == 1) ,
  Total = as.numeric(Session_1 == 1) + as.numeric(Session_2 == 1) + as.numeric(Session_3 == 1) + as.numeric(Session_4 == 1)
)

```

| Last updated: `r round(now())`
| The dataset contains `r length(unique(ds$ID))` unique participants with `r sum(ds$In_Person)` in-person sessions and `r sum(as.numeric(ds$Session_4 == 1))` Zoom sessions.
| `r sum(as.numeric(ds$Session_1 == 1 & ds$Session_2 == 1 & ds$Session_3 == 1))` participants have 3 complete in-person sessions.
| `r sum(ds$Total == 4)` participants have 4 complete sessions.
| `r sum(as.numeric(ds$Session_1 == 1 & ds$Session_2 == 1))` participants have complete 7 and 9 month sessions.
| `r sum(as.numeric(ds$Session_2 == 1 & ds$Session_3 == 1))` participants have complete 9 and 11 month sessions.
| `r sum(as.numeric(ds$Session_3 == 1 & ds$Session_4 == 1))` participants have complete 11 and 13 month sessions.
| 
| &#x2714; Complete, &#x2716; Pending, &#x274C; Missing/Unsure
| 

```{r}
#| echo: false

ds %>% select(-(next_interest_1:next_interest_4)) %>% 
reactable( 
          filterable = TRUE, 
          compact = TRUE,
          striped = TRUE,
          defaultPageSize = 50,
          defaultSorted = c("ID"),
          columns = list(
            ID = colDef(format = colFormat(digits = 0), maxWidth = 50, align = "left"),
            Session_1 = colDef(maxWidth = 90, cell = function(value) {if (value == 1) "\u2714\ufe0f" else if (value == 0) "\u274c" else "\u2716"}, footer = function(value) paste("Total:", sum(value==1))),
            Session_2 = colDef(maxWidth = 90, cell = function(value) {if (value == 1) "\u2714\ufe0f" else if (value == 0) "\u274c" else "\u2716"}, footer = function(value) paste("Total:", sum(value==1))),
            Session_3 = colDef(maxWidth = 90, cell = function(value) {if (value == 1) "\u2714\ufe0f" else if (value == 0) "\u274c" else "\u2716"}, footer = function(value) paste("Total:", sum(value==1))),
            Session_4 = colDef(maxWidth = 90, cell = function(value) {if (value == 1) "\u2714\ufe0f" else if (value == 0) "\u274c" else "\u2716"}, footer = function(value) paste("Total:", sum(value==1))),
             In_Person = colDef(maxWidth = 90),
             Total = colDef(maxWidth = 90)))

```
