---
title: "Summaries"
fig-dpi: 300
lightbox: auto
execute:
  cache: false
format: 
  html:
    toc: true
    code-fold: true
    code-tools: true
    code-link: true
knitr: 
  opts_chunk: 
    out.width: "100%"
---

```{r}
#| echo: false
#| warning: false
#| error: false

library(tidyverse)
library(hms)
library(rstatix)
library(flextable)
library(pins)

pal <-  c("#F0E442","#009E73","#56B4E9", "#E69F00","#0072B2") %>%  set_names(c("Standing", "Sitting", "Prone", "Supine", "Held"))
restraint_pal <-  c("#CC79A7","chartreuse4") %>%  set_names(c("Restrained", "Unrestrained"))

theme_update(text = element_text(size = 12),
             axis.text.x = element_text(size = 12, color = "black"), 
             axis.title.x = element_text(size = 14),
             axis.text.y = element_text(size = 12,  color = "black"), 
             axis.title.y = element_text(size = 14), 
             panel.background = element_blank(),panel.border = element_blank(), 
             panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(), axis.line = element_blank(), 
             axis.ticks.length=unit(.25, "cm"), 
             legend.key = element_rect(fill = "white")) 

board <- board_folder("/Volumes/padlab/study_sensorsinperson/data_processed/datasets/")
data_version <- board %>% pin_meta("imu_raw_samples")
ds <- board %>% pin_read("imu_raw_samples") %>%
  filter(nap_period == 0, exclude_period == 0)
```

| Last updated: `r round(now())` using pinned data version from: `r round(data_version$created)`
| Users can load data by running (requires one-time google drive authentication):
```{r}
#| eval: false
library(tidyverse)
library(pins)
library(nanoparquet)
library(googledrive)

# Load the board of pinned data sets (authenticated users only)
board <- board_gdrive(path = as_id("1OZlphhu6vYm1A2Bm2-zD7a4luS5nGWgS")) 

# To see available pinned data
board %>% pin_list()

# To read a specific data pin into memory
ds <- board %>% pin_read("imu_raw_samples") %>%
  filter(nap_period == 0, exclude_period == 0)
```

### Usable data

```{r}
#| warning: false
#| label: Usable-data
#| tbl-cap: Usable data and total recording length in hours

usable_data <- ds %>% count(id, session) %>% mutate(usable_hours = n/3600)
recording_duration <- ds %>% group_by(id, session) %>% 
  mutate(recording_hours = as.numeric(max(time) - min(time))) %>% 
  slice_head(n = 1) %>% ungroup
  
usable_data %>% left_join(recording_duration) %>% 
  get_summary_stats(usable_hours, recording_hours, show = c("mean", "sd","min","max")) %>% 
  flextable() %>% autofit()
```

```{r}
#| warning: false
#| label: Usable-data-histograms
#| layout-ncol: 2
#| fig-cap: 
#|   - "Usable hours after exclusions"
#|   - "Recording length in hours"
  
usable_data  %>% 
  ggplot(aes(x = usable_hours)) + 
  geom_histogram() + 
  scale_x_binned(name = "Hours", limits = c(2,14))

recording_duration  %>% 
  ggplot(aes(x = recording_hours)) + 
  geom_histogram() + 
  scale_x_binned(name = "Hours", limits = c(2,14))
```


### Infant Position Frequency by Age (Overall)

```{r} 
#| warning: false
#| label: position-table-age
#| tbl-cap: Position summary statistics

ds_sum <- ds %>% group_by(id, session) %>% 
  mutate(total_samples = n()) %>% group_by(id, session, pos) %>% 
  summarize(pos_n  = n(), total_samples = mean(total_samples)) %>% ungroup
ds_sum <- ds_sum %>% complete(nesting(id, session), pos, fill = list(pos_n = 0, total_samples = 1))
ds_sum$pos_prop = ds_sum$pos_n/ds_sum$total_samples*100
ds_sum$session = as.numeric(ds_sum$session)

ds_sum %>% group_by(pos, session) %>% 
  get_summary_stats(pos_prop, show = c("mean", "sd","min","max")) %>% 
  select(-variable) %>% flextable() %>% autofit()
```

```{r}
#| warning: false
#| label: "frequency-by-age-overall"
#| layout-ncol: 2
#| fig-cap: 
#|   - "Position means and SE"
#|   - "Position distribution"

ggplot(ds_sum, aes(x = session, y = pos_prop, color = pos)) + 
  stat_summary(position = position_dodge(.1)) + 
  stat_summary(geom = "line", position = position_dodge(.1)) + 
  ylim(0,101) + ylab("% of time") + xlab("Session") +
  scale_x_continuous(breaks = 1:3, labels = c("7 mo","9 mo","11 mo"), limits = c(0.5,3.5)) + 
  scale_color_manual(values = pal, name ="") + 
  theme(legend.position = "bottom")

ggplot(ds_sum, aes(x = session, y = pos_prop, fill = pos)) + 
  stat_summary(geom = "bar", position = "stack") + 
  ylim(0,101) + ylab("% of time") + xlab("Session") +
  scale_x_continuous(breaks = 1:3, labels = c("7 mo","9 mo","11 mo"), limits = c(0.5,3.5)) + 
  scale_fill_manual(values = pal, name ="") + 
  theme(legend.position = "bottom")
```

### Infant Position Frequency by Age (Individual)

```{r}
#| out-width: "90%"
#| warning: false
#| label: "frequency-by-age-individual"

ggplot(ds_sum, aes(x = session, y = pos_prop, color = pos, group = id)) + 
  facet_wrap(~ pos) + 
  geom_point() + geom_line() +  
  ylim(0,100) + ylab("% of time") + xlab("Session") +
  scale_x_continuous(breaks = 1:3, labels = c("7 mo","9 mo","11 mo"), limits = c(0.5,3.5)) + 
  scale_color_manual(values = pal, name ="") + 
  theme(legend.position = "none")
``` 

### Infant Restraint Frequency by Age (Overall)

```{r} 
#| warning: false
#| label: restraint-table-age
#| tbl-cap: Restraint summary statistics

ds_sum_restraint <- ds %>% group_by(id, session) %>% 
  mutate(total_samples = n()) %>% group_by(id, session, restraint) %>% 
  summarize(restraint_n  = n(), total_samples = mean(total_samples)) %>% ungroup
ds_sum_restraint <- ds_sum_restraint %>% complete(nesting(id, session), restraint, fill = list(restraint_n = 0, total_samples = 1))
ds_sum_restraint$restraint_prop = ds_sum_restraint$restraint_n/ds_sum_restraint$total_samples*100
ds_sum_restraint$session = as.numeric(ds_sum_restraint$session)

ds_sum_restraint %>% group_by(restraint, session) %>% 
  get_summary_stats(restraint_prop, show = c("mean", "sd","min","max")) %>% 
  select(-variable) %>% flextable() %>% autofit()
```
```{r}
#| warning: false
#| label: "restraint-by-age-overall"
#| layout-ncol: 2
#| fig-cap: 
#|   - "Restraint means and SE"
#|   - "Restraint distribution"

ggplot(ds_sum_restraint, aes(x = session, y = restraint_prop, color = restraint)) + 
  stat_summary(position = position_dodge(.1)) + 
  stat_summary(geom = "line", position = position_dodge(.1)) + 
  ylim(0,101) + ylab("% of time") + xlab("Session") +
  scale_x_continuous(breaks = 1:3, labels = c("7 mo","9 mo","11 mo"), limits = c(0.5,3.5)) + 
  scale_color_manual(values = restraint_pal, name ="") + 
  theme(legend.position = "bottom")

ggplot(ds_sum_restraint, aes(x = session, y = restraint_prop, fill = restraint)) + 
  stat_summary(geom = "bar", position = "stack") + 
  ylim(0,101) + ylab("% of time") + xlab("Session") +
  scale_x_continuous(breaks = 1:3, labels = c("7 mo","9 mo","11 mo"), limits = c(0.5,3.5)) + 
  scale_fill_manual(values = restraint_pal, name ="") + 
  theme(legend.position = "bottom")
```
### Infant Restraint Frequency by Age (Individual)

```{r}
#| out-width: "90%"
#| warning: false
#| label: "restraint-by-age-individual"

ggplot(ds_sum_restraint, aes(x = session, y = restraint_prop, color = restraint, group = id)) + 
  facet_wrap(~ restraint) + 
  geom_point() + geom_line() +  
  ylim(0,100) + ylab("% of time") + xlab("Session") +
  scale_x_continuous(breaks = 1:3, labels = c("7 mo","9 mo","11 mo"), limits = c(0.5,3.5)) + 
  scale_color_manual(values = restraint_pal, name ="") + 
  theme(legend.position = "none")
```
 
### Posture by restraint

```{r}
#| out-width: "90%"
#| warning: false
#| label: "posture-by-restraint"

ds_sum_posrest <- ds %>% group_by(id, session) %>% 
  mutate(total_samples = n()) %>% group_by(id, session, pos, restraint) %>% 
  summarize(posrest_n  = n()) %>% ungroup
ds_sum_posrest <- ds_sum_posrest %>% complete(nesting(id, session), restraint, pos, fill = list(posrest_n = 0))
ds_sum_posrest <- ds_sum_posrest %>% group_by(id, session) %>% 
  mutate(total_samples = sum(posrest_n)) %>% ungroup
ds_sum_posrest$prop = ds_sum_posrest$posrest_n/ds_sum_posrest$total_samples*100
ds_sum_posrest$session = as.numeric(ds_sum_posrest$session)

ggplot(ds_sum_posrest, aes(x = session, y = prop, color = pos)) + 
  stat_summary(position = position_dodge(.1)) + 
  stat_summary(geom = "line", position = position_dodge(.1)) + 
  facet_wrap(~ restraint) + 
  ylab("% of time") + xlab("Session") +
  scale_x_continuous(breaks = 1:3, labels = c("7 mo","9 mo","11 mo"), limits = c(0.5,3.5)) + 
  coord_cartesian(ylim = c(0,55)) + 
  scale_color_manual(values = pal, name ="") + 
  theme(legend.position = "bottom")
```

```{r}
#| warning: false
#| label: posture-restraint-table-age
#| tbl-cap: Posture by restraint summary statistics

ds_sum_posrest %>% group_by(session, pos, restraint) %>% 
  get_summary_stats(prop, show = c("mean", "sd","min","max")) %>% 
  select(-variable) %>% flextable() %>% autofit()
```
 