---
title: "Wear Time"
fig-dpi: 300
execute:
  cache: false
  error: false
  warning: false
  echo: false
format: 
  html:
    page-layout: custom
knitr: 
  opts_chunk: 
    out.width: "100%"
---

| Last updated: `r round(lubridate::now())`

These timelines are used to explore and make potential corrections to parent-logged wear time based on automatically-detected wear time based on sensor movement. Use the drop-down menu to select a session. The bottom timeline allows the user to select a range to zoom in. Each timeline can be dynamically panned, and hovering over the timeline indicates the data value. Values are smoothed over a 30-s window; each point represents the proportion of samples in the 30-s window labelled as "worn".

```{r}
#| echo: false
#| error: false
#| warning: false
library(tidyverse)
library(hms)
library(rstatix)
library(flextable)
library(pins)
library(plotly)
library(TTR)
library(crosstalk)

pal <-  c("#F0E442","#009E73","#56B4E9", "#E69F00","#0072B2") %>%  set_names(c("Standing", "Sitting", "Prone", "Supine", "Held"))
restraint_pal <-  c("#CC79A7","chartreuse4") %>%  set_names(c("Restrained", "Unrestrained"))

theme_update(text = element_text(size = 12),
             axis.text.x = element_text(size = 12, color = "black"), 
             axis.title.x = element_text(size = 14),
             axis.text.y = element_text(size = 12,  color = "black"), 
             axis.title.y = element_text(size = 14), 
             panel.background = element_blank(),panel.border = element_blank(), 
             panel.grid.major = element_blank(),
             panel.grid.minor = element_blank(), axis.line = element_blank(), 
             axis.ticks.length=unit(.25, "cm"), 
             legend.key = element_rect(fill = "white")) 

# lims <- as_hms(c('07:00:00', '21:59:00'))
# hour_breaks = as_hms(c('07:00:00','08:00:00','09:00:00', '10:00:00', '11:00:00', '12:00:00', '13:00:00', '14:00:00', '15:00:00', '16:00:00', '17:00:00', '18:00:00', '19:00:00', '20:00:00', '21:00:00'))
# label_breaks = c("7am","","9am","","11am","","1pm","","3pm","","5pm","","7pm","","9pm")

board <- board_folder("/Volumes/padlab/study_sensorsinperson/data_processed/datasets/")
data_version <- board %>% pin_meta("imu_raw_samples")
ds <- board %>% pin_read("imu_raw_samples") %>% 
  mutate(wear_status = as.numeric(wear_status == "worn"),
         wear_status_cg = as.numeric(cg_wear_status == "worn"),
         wear_status_cg = ifelse(is.na(wear_status_cg),0,wear_status_cg),
         logged_exclude = as.numeric(!(exclude_period == 1 | nap_period == 1)),
         logged_exclude_cg = as.numeric(cg_exclude_period == 0),
         logged_exclude_cg = ifelse(is.na(logged_exclude_cg), 1, logged_exclude_cg),
         id = as.numeric(id),
         session = as.numeric(session),
         id_uni = str_glue("{id}_{session}"))
ds$inf_wear = SMA(ds[,"wear_status"], 30)
ds$inf_excl = SMA(ds[,"logged_exclude"], 30)
ds$cg_wear = SMA(ds[,"wear_status_cg"], 30)
ds$cg_excl = SMA(ds[,"logged_exclude_cg"], 30)

ds <- ds %>% filter(row_number() %% 15 == 0)
shared_ds <- SharedData$new(ds)
```

```{r} 
#| error: false
#| warning: false
#| echo: false
shared_plot <- plot_ly(data = shared_ds, type = 'scatter', mode = 'lines') %>% 
  add_trace(x = ~time, y = ~inf_wear, name = "Sensor-based") %>% 
  add_trace(x = ~time, y = ~inf_excl, name = "Parent-logged") %>% 
  layout(xaxis = list(
    type = "date",
    title = "Time",
    tickformat = "%I:%M %p",
    rangeslider = list(visible = T)),
    yaxis = list(title = "Infant Wear Time"))

bscols(
  widths = c(1,1,9),
  list(),
  list(
    filter_select(
      id = "id_slider",
      label = "Session",
      sharedData = shared_ds,
      multiple = F,
      group = ~id_uni
      )
  ),
  list()
  )
bscols(
  widths = c(1,1,9),
  list(),
  list(),
  shared_plot
  )


```

```{r} 
#| error: false
#| warning: false
#| echo: false
shared_plot_cg <- plot_ly(data = shared_ds, type = 'scatter', mode = 'lines') %>% 
  add_trace(x = ~time, y = ~cg_wear, name = "Sensor-based") %>% 
  add_trace(x = ~time, y = ~cg_excl, name = "Parent-logged") %>% 
  layout(xaxis = list(
    type = "date",
    title = "Time",
    tickformat = "%I:%M %p",
    rangeslider = list(visible = T)),
    yaxis = list(title = "CG Wear Time"))

bscols(
  widths = c(1,1,9),
  list(),
  list(),
  shared_plot_cg
  )


```